Model Search in Relational Domains

### 2016-10-21 decision.tex
decision level
decision

\subsection{Decision}
A decision $\mathcal{D}$ is a meet irreducible that refines the 
current abstract valuation.  For example, a decision in interval 
domain can be of the form $\langle x R c \rangle$ where 
$R \in \{\leq, \geq\}$, $c$ is the bound.  A decision in 
relational domain such as octagon is of the form $ax - by \leq c$, 
where $x$ and $y$ are variables, $a,b \in \{-1,0,1\}$ are co-efficients, 
and $c \in \mathbb{R}\cup\{\infty\}$ is the bound of the inequality.  
That is, a decision can specify relation between variables, for example 
$\{x \leq y)$.  A decision must always be consistent with respect to 
the trail $\mathcal{T}$, that is, it must not contradict with the elements 
in the trail.

@@

Given a set of variables $\mathcal{V}$ and a current abstract value $v$, 
a decision phase heuristically returns a non-singleton meet irreducible 
by choosing a set of branching variables $\{B\} \subseteq \mathcal{V}$, 
a bound $c$, and a polarity ($\leq$ or $\geq$).  For interval domain, $|B|=1$.  
A decision changes the sate of the solver by adding a new meet irreducible 
$m$ and labelling information $s=decision$ to the trail, which is described below. 
\[decide: \quad (\mathcal{E},S) \rightarrow (\mathcal{E}(m,s),S) \]

@@

ACDCL supports several decision heuristics namely, {\em ordered}, 
{\em longest-range}, {\em random}, {\em relational} and 
{\em Berkmin}~\cite{eugoldberg07} decision heuristics.  
The {\em ordered} decision heuristics creates an ordering among non-singleton 
meet irreducibles, thereby making decisions on meet irreducibles that involve 
conditional variables (variables that appear in conditional branches) first 
before choosing meet irreducibles with numerical variables.  
The ordering is path-sensitive as it gives an effect of trace partitioning.

>>>>

\subsection{Decision}
A decision $\mathcal{D}$ is a meet irreducible that refines the 
current abstract valuation.  For example, a decision in interval 
domain can be of the form $\langle x R c \rangle$ where 
$R \in \{\leq, \geq\}$, $c$ is the bound.  A decision in 
relational domain such as octagon is of the form $ax - by \leq c$, 
where $x$ and $y$ are variables, $a,b \in \{-1,0,1\}$ are co-efficients, 
and $c \in \mathbb{R}\cup\{\infty\}$ is the bound of the inequality.  
That is, a decision can specify relation between variables, for example 
$\{x \leq y)$.  A decision must always be consistent with respect to 
the trail $\mathcal{T}$, that is, it must not contradict with the elements 
in the trail.  A new decision always increases the decision level by one.

@@

Given a set of variables $\mathcal{V}$ and a current abstract value $v$, 
a decision phase heuristically returns a non-singleton meet irreducible 
over a set of branching variables $\{B\} \subseteq \mathcal{V}$, a 
bound $c$, and a polarity ($\leq$ or $\geq$).  For interval domain, $|B|=1$ 
since an interval meet irreducible is defined over a single variable.  For 
octagons, $|B|=2$.  A decision adds a new meet irreducible $m$ to the trail.  
Subsequently, the new state of the solver is defined over $m$ and corresponding 
label information $s=decision$, which is described below. 
\[decide: \quad (\mathcal{E},S) \rightarrow (\mathcal{E}(m,s),S) \]

@@

ACDCL supports several decision heuristics namely, {\em ordered}, 
{\em longest-range}, {\em random}, {\em relational} and 
{\em Berkmin}~\cite{eugoldberg07} decision heuristics.  
The {\em ordered} decision heuristics creates an ordering among non-singleton 
meet irreducibles, thereby making decisions on meet irreducibles that involve 
conditional variables (variables that appear in conditional branches) first 
before choosing meet irreducibles with numerical variables.  
The ordering heuristic is similar to trace partitioning~\cite{toplas07}.
